\begin{abstract}

    % A code smell is a code-design issue that can lead to decrease in code
    % quality, thereby hindering developers from reading or maintaining a
    % software program.
    %
    Code smell detection tools help developers by automatically checking for the
    existence of code anti-patterns that may compromise software quality.
    %
    % Code smell detection tools have the potential to be language-independent,
    % because common code smells occur in many different programming languages.
    % % A language-independent code smell detector can set unified detection
    % rules across programming languages, which is especially useful in
    % multi-language software development. % However, few code smell detection
    % tools support multiple programming languages.
    %
    Despite the prevalence of common code smells across various programming
    languages, there is a noticeable need for language-independent tools that
    consistently perform code smell detection for both multiple- and
    single-language projects.
    %
    % Despite both the prevalence of common code smells across various programming
    % languages and the need for tools that consistently perform code smell detection
    % for both multiple- and single-language projects, there is a noticeable lack of
    % such tools that support multiple programming languages.
    %
    Filling the aforementioned gap, this paper presents a tool, called
    \texttt{TreeNose}, that leverages well-established Treesitter source code
    parsers to detect smells across programming languages.
    The presented tool automatically finds 5 types of code smells across 3
    languages (i.e., Python, Java, and JavaScript) and its adoption of Treesitter
    parsers ensures extensibility.
    This paper empirically answers three research questions to explore
    \texttt{TreeNose}'s effectiveness and to characterize the manifestation of code
    smells in different languages.
    Performing a manual annotation study, we used 9 open-source projects to compare
    \texttt{TreeNose} to language-specific code smell detectors, ultimately
    revealing that \texttt{TreeNose}'s classifications lead to an F1 score of 0.94.
    %
    % 9 open-source projects implemented in the 3 chosen
    % languages, comparing through a manual annotation traditional, language-specific
    % code smell detectors in a .
    %
    % We applied \texttt{TreeNose} to 16 open-source projects implemented in
    % the 3
    % chosen languages and the combinations of those languages,
    % comparing its results
    %
    % The results from this study
    %
    Augmenting the 9 projects with 7 more, including 4 projects that are
    multi-language in nature, revealed that the Complex Conditional smell comprises
    between 32\% and 51\% of the detected code smells.
    %
    % The experiments also revealed that the Complex Conditional smell comprises
    %
    The results also showed that Long Method smells make up 38\% of all those
    detected for JavaScript programs and Long Class code smells constitute 30\% of those
    found in Java programs.
    Finally, the experiments uncovered evidence of each programming language having
    code smells that are more common for it than the other studied languages.
    %
    % that are significantly more common than the languages, suggesting
    % a connection between code smells and programming languages.
    % % that
    % % they have strong tendencies to have specific code smells.

\end{abstract}
