\vspace*{-0.5em}

\section{Background and Related Work}~\label{sec:background}

\vspace*{-1em}

% Explain the basics of code smells and their importance and prevalence

{\bf Code Smells}. Originating from Fowler and Beck's \textit{Refactoring} book,
code smells are important considerations for both researchers and practitioners.
The research community has defined numerous code smells
\cite{Pysmell,SQLAntipatterns,CleanCode,RefactoringWorkbook}, with Jerzyk
recently releasing an online catalog with 56 common code smells
\cite{Jerzyk2023}. At the same time, community was also exploring the
characteristics of code smells. Yamashita conducted several empirical studies to
investigate the effects of code smells on maintainability \cite{6392174}
\cite{6405287}. She also conducted another study to discover developers' opinion
of code smells \cite{developersCare}, where she discoverd the top 15 most common
code smells in developers' perception. Researchers, like Tufano
\cite{whenandwhy} and Peters \cite{lifespan}, conducted studies to discover the
characteristics of code smells in lifespan of software projects. Santana, Cruz,
and, Figueiredo found the strong agglomerations of certain code smells highly
occur in software projects \cite{Santana}. Pascarella found active code reviews
significantly reduce the severity of code smells \cite{Pascarella}.

{\bf Code Smell Detection}. Because of the negative impact of code smells on
software projects, developers acknowledge the importance of detecting them. The
manual code smell detection was proven to be error-prone and resource-consuming
\cite{DetectingDefectsInObject}. Therefore, code smell detection tools have been
developed to automate this process. Different code smell detection tools rely on
various detection strategies, such as abstract syntax tree (AST) analysis,
Machine Learning, and Static Analysis. Van Emden and Moonen built the first code
smell detection tool in Java \cite{1173068}. Since then, many language-specific
code smell detection tools have been developed, such as PMD \cite{PMD} and
CheckStyle \cite{CheckStyle}. Chen \cite{Pysmell} built a code smell detection
tool in Python targeting on Python specific code smells. All the tools mentioned
above rely on AST to detect code smells. Except AST-based detection, There are
also developers utilizing approaches like Machine Learning and textual
components. For example, Pontillo utilized Machine Learning to detect test
smells, similar to code smell, to achieve better performance than
heuristic-based techniques, but had a challenge of overcoming F1 score of 0.51.
Palomba el al. designed a text-based code smell technique to detect code smells
and found the benefits of combining textual and structural information in code
smell detection \cite{Palomba}.

% \subsection{Code Smell in Multi-Language System}

{\bf Multi-Language Code Smells}. It's one feature of modern software
development to use multiple programming languages~\cite{723183}. Developers
utilize multiple programming languages to leverage their
strengths~\cite{7476675}.
%
Common code smells are broadly recognized across programming languages
\cite{PMD,CheckStyle,Pysmell,Jscent,DesigniteJava}. There are also researchers
who have conducted studies to investigate code smells in multi-language systems.
Abidi et al. defined 12 multi-language design smells (i.e., code smells and
anti-patterns) \cite{MultiLanguageCodeSmells}. They discovered that
multi-language code smells commonly raise during the maintenance and refactoring
activities and have a strong negative impact on software quality \cite{Abidi2}.
They also built a multi-system code smell detection tool with srcML (a
multi-language parsing tool to convert source code into XML), to detect design
smells in multi-language systems. They suggested that multi-language design
smells are prevalent in multi-language systems and have a strong negative impact
on software readability \cite{Fault-Prone}. Nagy and Cleve built a SQL code
smell detection tool for SQL statements embedded in Java code \cite{SQLInJava}.
