\section{Conclusions and Future Work}

% Removed this text and replace it with content that is a little shorter:

% with an annotation study in three programming language system, i.e., Java,
% JavaScript, and Python, and compared it with other language-specific tools in
% a set of high-quality open-source projects in target programming languages.

% As a result, \texttt{TreeNose} achieved a high level of
% accuracy with 0.94 F1 score in detecting selected code smells. As a comparison,
% the combination of other tools achieved 0.48 F1 score. We concluded
% \texttt{TreeNose} is an effective tool for detecting code smells across
% programming language systems. We also analyzed the distribution and prevalence
% of code smells in the programming language systems with \texttt{TreeNose}.

% Review the TreeNose tool, experimental setup, and the results

This paper presents \texttt{TreeNose}, a language-independent code smell
detection tool that leverages industry-standard Treesitter parsers.
\texttt{TreeNose} detects 5 code smells that other language-specific tools
(e.g., PySmell and JScent) commonly support: Complex Conditional (CC), Long
Class (LC), Long Method (LM), Long Method Chain (LMC), and Long Parameter List
(LPL).
%
Using a manual annotation study, we compared the scores arising from
\texttt{TreeNose}'s code smell classifications to those made with the
language-specific smell detectors for Java, JavaScript, and Python.
%
This experiment revealed that the classifications with the language-specific
tools yield an F1 score of 0.48 in comparison to \texttt{TreeNose}'s
classifications leading to an F1 score of 0.94.



%
As results of the analysis, we found that 1. Complex Conditional (CC) is the
most common code smell across programming languages with 42\% average
proportion. 2. Programming languages have strong tendencies in some code smells
with at least 1 time worse performance than others. 3. systems written in
multi-language have weaker tendencies in code smells compared to the single
language systems with zero negative values less than - 1.0.

In the future, we plan to extend \texttt{TreeNose} to detect more code smells
and evaluate it with more programming language systems. As for annotation, we
plan to conduct studies with more participants and subjects to increase the
reliability of the results. We also wish to implement \texttt{TreeNose} in a
real-world software development environment to see how it can help developers
maintain the quality of their codebase.
